%-------------------------
% One-Page Resume in LaTeX
% Author: Nikhil Sharma
% Target Role: Software Development Engineer (SDE-1)
%-------------------------

\documentclass[letterpaper,10.5pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\textheight}{0.75in}

\urlstyle{same}
\raggedbottom
\raggedright

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADER-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nikhil Sharma} & \href{mailto:nsharma@ce.iitr.ac.in}{nsharma@ce.iitr.ac.in} \\
  Contact: +91 7310534041 & \href{https://www.linkedin.com/in/nikhil-sharma}{linkedin.com/in/nikhil-sharma} \\
  \href{https://github.com/nik-shar}{github.com/nik-shar} & \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\small{
AI Engineer specializing in production-grade LLM systems, agent orchestration, and retrieval-augmented generation (RAG). Experienced in building deterministic agent pipelines, hybrid retrieval systems, and deploying scalable AI services on GCP with reliability-focused safeguards.
}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Turing}{Remote}
{Delivery Data Scientist (Full-Time)}{Jun 2025 -- Present}
\resumeItemListStart
  \resumeItem{Data Curation Pipelines}
    {Designed and executed structured human-in-the-loop workflows for LLM training datasets, including QA pairs, video event annotations, and LaTeX/HTML extraction.}
  \resumeItem{Data Validation}
    {Built Python-based preprocessing and JSON schema validation pipelines to improve annotation consistency and downstream model readiness.}
  \resumeItem{Quality and Alignment}
    {Performed dataset auditing, error taxonomy analysis, and consistency checks; collaborated with ML and product teams to align data contracts with training and inference requirements.}
\resumeItemListEnd

\resumeSubheading
{Avkalan Labs}{Remote}
{IoT Machine Learning Engineer Intern}{May 2024 -- Aug 2024}
\resumeItemListStart
  \resumeItem{Edge AI Deployment}
    {Deployed ML models on ESP32 using TensorFlow Lite for Microcontrollers and \texttt{emlearn} for real-time inference.}
  \resumeItem{Optimization}
    {Optimized memory footprint and inference latency; implemented quantization and firmware-level pipeline improvements for constrained hardware.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Taskchain Agent Orchestrator (LLM + RAG)}{}
{Personal Project}{2025 -- Present}
\resumeItemListStart
  \resumeItem{Agentic Workflow Backend}
    {Architected a strict \texttt{plan -> retrieve -> execute -> verify} pipeline using FastAPI and LangGraph for deterministic, auditable execution.}
  \resumeItem{Schema-Safe Tooling}
    {Enforced schema-validated tool calls with Pydantic to prevent malformed execution and reduce hallucinated actions.}
  \resumeItem{Hybrid Retrieval}
    {Implemented hybrid retrieval with SQLite FTS5 (lexical) and Chroma embeddings (semantic), plus deterministic fallback logic for reliability.}
  \resumeItem{Verification and Observability}
    {Added evidence/citation verification gates, execution telemetry, and PostgreSQL run artifact persistence (\texttt{tasks}, \texttt{task\_runs}) for debugging and evaluation.}
  \resumeItem{Cloud Deployment}
    {Deployed on Google Cloud Run with Cloud SQL, Secret Manager, and Cloud Build; added unit/integration tests for deterministic and LLM fallback behavior.}
\resumeItemListEnd

\resumeSubheading
{IoT Sensor Data Aggregation and Visualization Platform}{}
{Personal Project}{Jan 2025 -- Present}
\resumeItemListStart
  \resumeItem{Backend and APIs}
    {Built a FastAPI backend for real-time ESP32 sensor stream ingestion with modular REST APIs and multi-node communication.}
  \resumeItem{Frontend Monitoring}
    {Developed a React.js dashboard for live visualization and monitoring with scalable backend integration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
\resumeSubHeadingListStart

\resumeSubheading
{Technical Head}{Models and Robotics Section, IIT Roorkee}
{Student Leadership Role}{May 2024 -- Present}
\resumeItemListStart
  \resumeItem{Team Leadership}
    {Led a 50+ member technical team and managed an INR 4L annual budget for robotics R\&D and competitions.}
  \resumeItem{Community Initiatives}
    {Organized national-level hackathons and technical workshops; secured \textbf{1st Prize in Ware Wizard (Cognizance, IIT Roorkee)}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------COMPETITIVE PROGRAMMING-----------------
\section{Competitive Programming}
\resumeSubHeadingListStart
\resumeSubheading
{LeetCode and GeeksforGeeks}{}{}{Jul 2024 -- Present}
\resumeItemListStart
  \resumeItem{Problem Solving}
    {Solved 400+ algorithmic problems; achieved max LeetCode rating of 1787.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Programming}{Python, SQL}
  \resumeSubItem{Machine Learning \& AI}{RAG Systems, Agentic Workflows, LLM Tool Calling, Retrieval Evaluation, Model Quantization, TensorFlow Lite Micro}
  \resumeSubItem{LLM \& Retrieval Systems}{LangGraph, OpenAI API, Embedding-based Retrieval, Hybrid Search (FTS5 + Vector DB), Chroma, Prompt Engineering}
  \resumeSubItem{Backend \& Data Systems}{FastAPI, Pydantic, REST APIs, PostgreSQL, SQLite (FTS5), JSON Schema Validation}
  \resumeSubItem{Cloud \& DevOps}{Docker, Google Cloud Run, Cloud SQL, Secret Manager, Cloud Build, Git, Linux}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Technology, Roorkee}{Roorkee, India}
{B.Tech in Civil Engineering}{Nov 2021 -- May 2025}
\resumeSubHeadingListEnd

\end{document}
